### 2017-11-02 submission/manuscript.Rmd
add thrid paragraph

The driver-passenger model of the microbial role in CRC, as summarized by Flynn [@flynn_metabolic_2016], can be supported with this data for carcinoma but not necessarily for adenoma. The drasitically increased relative risk of disease when considering the CRC associated genera is highly supportive of this type of process. In a driver-passenger scenario it is possible that simply having the driver present or only identifying the passenger is a good enough proxy that the event is occuring. This would account for the observation that there is no synergistic incrase in relative risk when accounting for either the total number or increasing abundance of these genera. The initial establishment of the driver within the system is also dependent on the community that is present and this could explain why adding the community context to our models increases the prediction. 
Although the driver-passenger model fits well with the transtion of adenoma to carcinoma for our carcinoma observations it does not fit well with our observed data on control to adenoma.

- Builiding on this idea moving forward how CRC associated genera interact with the overall community rather than in isolation will be important since they do not increase the RR of polyps
  - suggesting localized changes to community may be more important

>>>>

The driver-passenger model of the microbial role in CRC, as summarized by Flynn [@flynn_metabolic_2016], can be supported with this data for carcinoma but not necessarily for adenoma. The drasitically increased relative risk of disease when considering the CRC associated genera is highly supportive of this type of process. In a driver-passenger scenario it is possible that simply having the driver present or only identifying the passenger is a good enough proxy that the event is occuring. This would account for the observation that there is no synergistic incrase in relative risk when accounting for either the total number or increasing abundance of these genera. The initial establishment of the driver within the system is also dependent on the community that is present and this could explain why adding the community context to our models increases the prediction.

Our carcinoma observations fit the driver-passenger model and support this concept within the framework of the transition from adenoma to carcinoma. In contrast, the adenoma observations do not fit well with this model and suggests that the transition from control to adenoma do not fit this framework. The stepwise decrease in diversity suggests that the adenoma community is not normal but this change is subtle. Although there may be localized changes that do depend on the driver-passenger model, our observations show that they do not involve the CRC associated genera. It is possible to hypothesize that at early stages of the diease how the host interacts to these subtle changes could be the catlyst that causes adenoma formation. Subsequent transition to carcinoma could then fit into the proposed driver-passenger model framework.

### 2017-11-02 submission/manuscript.tex
add thrid paragraph

The driver-passenger model of the microbial role in CRC, as summarized
by Flynn {[}1{]}, can be supported with this data for carcinoma but not
necessarily for adenoma. The drasitically increased relative risk of
disease when considering the CRC associated genera is highly supportive
of this type of process. In a driver-passenger scenario it is possible
that simply having the driver present or only identifying the passenger
is a good enough proxy that the event is occuring. This would account
for the observation that there is no synergistic incrase in relative
risk when accounting for either the total number or increasing abundance
of these genera. The initial establishment of the driver within the
system is also dependent on the community that is present and this could
explain why adding the community context to our models increases the
prediction. Although the driver-passenger model fits well with the
transtion of adenoma to carcinoma for our carcinoma observations it does
not fit well with our observed data on control to adenoma.

\begin{itemize}
\item
  Builiding on this idea moving forward how CRC associated genera
  interact with the overall community rather than in isolation will be
  important since they do not increase the RR of polyps
\item
  suggesting localized changes to community may be more important
\item
  In closing to get at these more difficult questions the Power
  calculations and effect size in future studies need to be accounted
  for especially for adenoma where the predicted effect sizes are going
  to be small
\end{itemize}

>>>>

The driver-passenger model of the microbial role in CRC, as summarized
by Flynn {[}1{]}, can be supported with this data for carcinoma but not
necessarily for adenoma. The drasitically increased relative risk of
disease when considering the CRC associated genera is highly supportive
of this type of process. In a driver-passenger scenario it is possible
that simply having the driver present or only identifying the passenger
is a good enough proxy that the event is occuring. This would account
for the observation that there is no synergistic incrase in relative
risk when accounting for either the total number or increasing abundance
of these genera. The initial establishment of the driver within the
system is also dependent on the community that is present and this could
explain why adding the community context to our models increases the
prediction.

Our carcinoma observations fit the driver-passenger model and support
this concept within the framework of the transition from adenoma to
carcinoma. In contrast, the adenoma observations do not fit well with
this model and suggests that the transition from control to adenoma do
not fit this framework. The stepwise decrease in diversity suggests that
the adenoma community is not normal but this change is subtle. Although
there may be localized changes that do depend on the driver-passenger
model, our observations show that they do not involve the CRC associated
genera. It is possible to hypothesize that at early stages of the diease
how the host interacts to these subtle changes could be the catlyst that
causes adenoma formation. Subsequent transition to carcinoma could then
fit into the proposed driver-passenger model framework.

\begin{itemize}
\tightlist
\item
  In closing to get at these more difficult questions the Power
  calculations and effect size in future studies need to be accounted
  for especially for adenoma where the predicted effect sizes are going
  to be small
\end{itemize}
